Mergeable Types

### 2017-02-28 paper/implementation.tex

Importantly, Irmin supports user-defined three-way merge functions to
reconcile concurrent operations.  While Irmin's merge functions are defined
over objects on Irmin's content-addressable heap, \name's merge functions are
defined over OCaml types. We address this representational mis-match with the
help of OCaml's PPX metaprogramming support~\cite{ppx} to derive bi-directional
transformations between objects on OCaml and Irmin heaps. We also derive the
various serialization functions required by Irmin. This address the representation
mismatch between the application and storage layers. Synchronization between
replicas is performed using Git's notion of pushing and pulling updates from
remotes over the Git transfer protocol~\cite{git-tp}. As a result, we reap the
benefits of efficient delta-transfer (only missing objects are transferred
between replicas), compression and end-to-end encrypted communication between
the replicas.

>>>>

Importantly, Irmin supports user-defined three-way merge functions for
reconciling concurrent operations. While Irmin's merge functions are
defined over objects on Irmin's content-addressable heap, \name's
merge functions are defined over OCaml types. We address this
representational mismatch with the help of OCaml's PPX metaprogramming
support~\cite{ppx} to derive bi-directional transformations between
objects on OCaml and Irmin heaps. We also derive the various
serialization functions required by Irmin\footnote{
  The Since \nameMonad monad relies on Irmin for realizing the branch
  structure, it is in fact parameterized over a mergeable type that
  implements all these functions. Thus the monad is functorized over
  the mergeable type, but not polymorphic. The convenience of type
  parameter inference that polymorphism offers can however be obtained
  for module parameters using OCaml extensioms, such as Modular
  Implicits~\cite{implicits}.
}.
Synchronization between replicas is performed using Git's notion of
pushing and pulling updates from remotes over the Git transfer
protocol~\cite{git-tp}. As a result, we reap the benefits of efficient
delta-transfer (only missing objects are transferred between
replicas), compression and end-to-end encrypted communication between
he replicas.
